{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-03 Paper/main.tex
Small questions

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic bspline basis-function $\{5,6,...,18\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used the prediction RMSE calculated by 10 fold cross-validation.
		 To obtain valid out of sample properties for the FPCR, within each of the ten 10 fold cross-validation splits, we first calculate the Functional Principal Components of the trainig-set $\mathcal{T}$ for each curve. These scores are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation:

		 {\color{blue} We should mention how we derived the original principal components. (bspline basis and number of basis functions and harmonics.) As we chose a high number for both to capture all features of the data set. As we explain the approximations for the estimation, this question could come up, so we have to make it specific.}

@@

	\paragraph{Monomial Basis}
	Due to the high collinearity of these basis, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant. For reasons outlined in {\color{green} Link chapter}, they are suited for the smooth function $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios. This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less strongly pronounced.

>>>>

		where $Z \sim \mathcal{N}(0,1)$. In total, we created four combinations for the simulations, using the two true coefficient functions and the two sets of responses. These four combinations are then used with a different number of monomial basis functions $ \in \{1,2, \dots, 6\}$, cubic bspline basis-function $\{5,6,...,18\}$ and fourier functions $\{1,3,...,25\}$ to predict the generated responses using the basis expansion approach and the FPCR approach. For the evaluation, we used the prediction MSE calculated by 10 fold cross-validation.
		 To obtain valid out of sample properties for the FPCR, within each of the ten 10 fold cross-validation splits, we first calculate the Functional Principal Components of the trainig-set $\mathcal{T}$ for each curve. These scores are then used to estimate the scores of the holdout set $\mathcal{H}$, $\hat{\xi}_{i}^{m, \mathcal{H}}$  by the equation:

		 {\color{orange}I guess we don't use the scores of the training set to estimate scores of test set but eigenfunction of traningset..}
		 {\color{blue} We should mention how we derived the original principal components. (bspline basis and number of basis functions and harmonics.) As we chose a high number for both to capture all features of the data set. As we explain the approximations for the estimation, this question could come up, so we have to make it specific.}

@@

	\paragraph{Monomial Basis}
	Due to the high collinearity of these basis{(\color{orange} How about stressing the higher order? Are they already highly correlated at lower orders?)}, simulations were conducted up until the sixth monomial basis, excluding the first one since this just represents a constant. For reasons outlined in {\color{green} Link chapter}, they are suited for the smooth function $f_1$ and show a better performance than bsplines for this coefficient function, but show the weakest performance for the coefficient function $f_2$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) monomial basis functions for the high(low) signal-to-noise ratios. This weakness is especially pronounced in the setup $f_2,Y_1$; for the high noise setup, $f_2, Y_2$ this weakness is still visible, but less strongly pronounced.
